Supplementary Materials for Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019

### 2022-12-07 products/paper/supp_materials.qmd
Correct typo

```{r}
#| results: asis
#| label: tbl-full-models
#| tbl-cap: Log-odds ratios from full models predicting a student being clearly behind expected grade. All models used sample weights and adjust for design effects from sample weight variance and clustering of students within the same household.
texreg(lapply(list(model0_summary, model1_summary, model2_summary, 
                   model3_summary, model4_summary), convert_model),
       digits = 3,
       longtable = TRUE,
       use.packages = FALSE,
       caption.above = TRUE,
       custom.coef.names = 
         c("Intercept","Black","Indigenous","Asian","Latino","Black/White",
           "Black/Indigenous","Black/Latino", "Black/Asian",
           "White/Indigenous","White/Latino","White/Asian",
           "Indigenous/Latino","Indigenous/Asian","Latino/Asian",
           "Year (2010 origin)", "1st grade","2nd grade","3rd grade",
           "4th grade","5th grade","6th grade","7th grade","8th grade",
           "9th grade","10th grade","11th grade","12th grade","Alaska",
           "Arizona","Arkansas","California","Colorado","Connecticut",
           "Washington DC","Delaware","Florida","Georgia","Hawaii","Idaho",
           "Illinois","Indiana","Iowa","Kansas","Kentucky","Louisiana",
           "Maine","Maryland","Massachusetts","Michigan","Minnesota",
           "Mississippi","Missouri","Montana","Nebraska","Nevada",
           "New Hampshire","New Jersey","New Mexico","New York",
           "North Carolina","North Dakota","Ohio","Oklahoma","Oregon",
           "Pennsylvania","Rhode Island","South Carolina","South Dakota",
           "Tennessee","Texas","Utah","Vermont","Virginia","Washington",
           "West Virginia","Wisconsin","Wyoming","Non-metro","Central city",
           "Metro non-central","Metro indeterminable","Female",
           "Year x 1st grade","Year x 2nd grade","Year x 3rd grade",
           "Year x 4th grade","Year x 5th grade","Year x 6th grade",
           "Year x 7th grade","Year x 8th grade","Year x 9th grade",
           "Year x 10th grade","Year x 11th grade","Year x 12th grade",
           "Foreign-born","Mother foreign-born","Father foreign-born",
           "Speaks English somewhat", "Speaks English well", 
           "Mother speaks somewhat", "Mother speaks well",
           "Father speaks somewhat", "Father speaks well",
           "Mother High school diploma", "Mother AA degree", 
           "Mother BA degree","Mother Grad degree",
           "Father High school diploma", "Father AA degree", 
           "Father BA degree","Father Grad degree",
           "Family income (10K USD, sq. root)", "Owns home",
           "parents married"),
       groups = list("Race (ref. White)"=2:15, 
                     "Grade (ref. Kindergarten)"=17:28,
                     "State (ref. Alabama)"=29:78,
                     "Location (ref. Indeterminable)"=79:82,
                     "English proficiency (ref. none)"=99:100,
                     "Mother's English proficiency (ref. none)"=101:102,
                     "Father's English proficiency (ref. none)"=103:104,
                     "Mother's highest degree (ref. none)"=105:108,
                     "Father's highest degree (ref. none)"=109:112))
```

@@

```{r}
#| label: tbl-desc-stats-cult
#| tbl-cap: Cuiltural resources by race. Shading indicates biracial group. All results apply survey weights.
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(f_born=round(survey_mean(foreign_born, vartype = NULL), 3)*100,
            father_fb=round(survey_mean(foreign_born_father, 
                                        vartype = NULL), 3)*100,
            mother_fb=round(survey_mean(foreign_born_mother, 
                                        vartype = NULL), 3)*100,
            spk_eng_no=round(survey_mean(spk_eng=="No", vartype = NULL), 3)*100,
            spk_eng_some=round(survey_mean(spk_eng=="Somewhat", 
                                           vartype = NULL), 3)*100,
            spk_eng_yes=round(survey_mean(spk_eng=="Yes", vartype = NULL), 3)*100,
            f_spk_eng_no=round(survey_mean(spk_eng_father=="No", 
                                           vartype = NULL), 3)*100,
            f_spk_eng_some=round(survey_mean(spk_eng_father=="Somewhat", 
                                             vartype = NULL), 3)*100,
            f_spk_eng_yes=round(survey_mean(spk_eng_father=="Yes", 
                                            vartype = NULL), 3)*100,
            m_spk_eng_no=round(survey_mean(spk_eng_mother=="No", 
                                           vartype = NULL), 3)*100,
            m_spk_eng_some=round(survey_mean(spk_eng_mother=="Somewhat", 
                                             vartype = NULL), 3)*100,
            m_spk_eng_yes=round(survey_mean(spk_eng_mother=="Yes", 
                                            vartype = NULL), 3)*100)

>>>>

```{r}
#| results: asis
#| label: tbl-full-models
#| tbl-cap: Log-odds ratios from full models predicting a student being clearly behind expected grade. All models used sample weights and adjust for design effects from sample weight variance and clustering of students within the same household.
wordreg(lapply(list(model0_summary, model1_summary, model2_summary, 
                   model3_summary, model4_summary), convert_model),
       digits = 3,
       longtable = TRUE,
       use.packages = FALSE,
       caption.above = TRUE,
       file="full_reg.doc",
       custom.coef.names = 
         c("Intercept","Black","Indigenous","Asian","Latino","Black/White",
           "Black/Indigenous","Black/Latino", "Black/Asian",
           "White/Indigenous","White/Latino","White/Asian",
           "Indigenous/Latino","Indigenous/Asian","Latino/Asian",
           "Year (2010 origin)", "1st grade","2nd grade","3rd grade",
           "4th grade","5th grade","6th grade","7th grade","8th grade",
           "9th grade","10th grade","11th grade","12th grade","Alaska",
           "Arizona","Arkansas","California","Colorado","Connecticut",
           "Washington DC","Delaware","Florida","Georgia","Hawaii","Idaho",
           "Illinois","Indiana","Iowa","Kansas","Kentucky","Louisiana",
           "Maine","Maryland","Massachusetts","Michigan","Minnesota",
           "Mississippi","Missouri","Montana","Nebraska","Nevada",
           "New Hampshire","New Jersey","New Mexico","New York",
           "North Carolina","North Dakota","Ohio","Oklahoma","Oregon",
           "Pennsylvania","Rhode Island","South Carolina","South Dakota",
           "Tennessee","Texas","Utah","Vermont","Virginia","Washington",
           "West Virginia","Wisconsin","Wyoming","Non-metro","Central city",
           "Metro non-central","Metro indeterminable","Female",
           "Year x 1st grade","Year x 2nd grade","Year x 3rd grade",
           "Year x 4th grade","Year x 5th grade","Year x 6th grade",
           "Year x 7th grade","Year x 8th grade","Year x 9th grade",
           "Year x 10th grade","Year x 11th grade","Year x 12th grade",
           "Foreign-born","Mother foreign-born","Father foreign-born",
           "Speaks English somewhat", "Speaks English well", 
           "Mother speaks somewhat", "Mother speaks well",
           "Father speaks somewhat", "Father speaks well",
           "Mother High school diploma", "Mother AA degree", 
           "Mother BA degree","Mother Grad degree",
           "Father High school diploma", "Father AA degree", 
           "Father BA degree","Father Grad degree",
           "Family income (10K USD, sq. root)", "Owns home",
           "parents married"),
       groups = list("Race (ref. White)"=2:15, 
                     "Grade (ref. Kindergarten)"=17:28,
                     "State (ref. Alabama)"=29:78,
                     "Location (ref. Indeterminable)"=79:82,
                     "English proficiency (ref. none)"=99:100,
                     "Mother's English proficiency (ref. none)"=101:102,
                     "Father's English proficiency (ref. none)"=103:104,
                     "Mother's highest degree (ref. none)"=105:108,
                     "Father's highest degree (ref. none)"=109:112))
```

@@

```{r}
#| label: tbl-desc-stats-cult
#| tbl-cap: Cultural resources by race. Shading indicates biracial group. All results apply survey weights.
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(f_born=round(survey_mean(foreign_born, vartype = NULL), 3)*100,
            father_fb=round(survey_mean(foreign_born_father, 
                                        vartype = NULL), 3)*100,
            mother_fb=round(survey_mean(foreign_born_mother, 
                                        vartype = NULL), 3)*100,
            spk_eng_no=round(survey_mean(spk_eng=="No", vartype = NULL), 3)*100,
            spk_eng_some=round(survey_mean(spk_eng=="Somewhat", 
                                           vartype = NULL), 3)*100,
            spk_eng_yes=round(survey_mean(spk_eng=="Yes", vartype = NULL), 3)*100,
            f_spk_eng_no=round(survey_mean(spk_eng_father=="No", 
                                           vartype = NULL), 3)*100,
            f_spk_eng_some=round(survey_mean(spk_eng_father=="Somewhat", 
                                             vartype = NULL), 3)*100,
            f_spk_eng_yes=round(survey_mean(spk_eng_father=="Yes", 
                                            vartype = NULL), 3)*100,
            m_spk_eng_no=round(survey_mean(spk_eng_mother=="No", 
                                           vartype = NULL), 3)*100,
            m_spk_eng_some=round(survey_mean(spk_eng_mother=="Somewhat", 
                                             vartype = NULL), 3)*100,
            m_spk_eng_yes=round(survey_mean(spk_eng_mother=="Yes", 
                                            vartype = NULL), 3)*100)
